A systematic search for transiting planets in the \KT\ data

### 2015-02-15 ms.tex
words in the intro

This project follows in the tradition of independently implemented transit
search algorithms applied publicly available datasets \citep[such
as][]{petigura1, petigura2, roberto, dressing}.
These efforts have been hugely successful especially in the field of exoplanet
population inference because, thanks to their relative simplicity, the
efficiency and behavior of these pipelines can be quantified empirically.
The work described in this \paper\ is built on many of the same principles as
the previous projects built for studying \kepler\ data but our main
contribution is a framework for including a model of the systematic trends
into the search. \dfmtodo{blah}

@@

\Fig{completeness} shows the fraction of recovered signals as a function of
the physical parameters of the injection and the magnitude of the star.
As expected, the shallower transits at longer periods are recovered less
robustly.
It is worth noting that this figure is a two-dimensional projection (or
marginalization) of a higher dimensional measurement.
For example, this completeness map is conditioned on our assumptions about
the eccentricity distribution of planets and it is marginalized over the
empirical distribution of stellar parameters.
It is possible to relax this assumption and apply different distributions by
re-weighting the simulations used to generate this figure.
Therefore, alongside this \paper, we publish the full list of injection
simulations\footnote{SOMEURL} to be used for population inference (occurrence
rate measurements).
In \fig{completeness}, we also show the detection efficiency---marginalized
over the same range of periods---as a function of stellar magnitude in the
\kepler\ bandpass as reported in the EPIC \citep{epic}.

@@

>>>>

This project follows in the tradition of independently implemented transit
search algorithms applied publicly available datasets \citep[such
as][]{petigura1, petigura2, roberto, dressing}.
These efforts have been hugely successful especially in the field of exoplanet
population inference because, thanks to their relative simplicity, the
efficiency and behavior of these pipelines can be quantified empirically.
The work described in this \paper\ is built on many of the same principles as
the previous projects built for studying \kepler\ data but our main
intellectual contribution is a computationally tractable framework for
simultaneously fitting for the trends and the transit signal even when
searching for planets.

@@

\Fig{completeness} shows the fraction of recovered signals as a function of
the physical parameters of the injection and the magnitude of the star.
As expected, the shallower transits at longer periods are recovered less
robustly.
It is worth noting that this figure is a two-dimensional projection (or
marginalization) of a higher dimensional measurement.
For example, this completeness map is conditioned on our assumptions about
the eccentricity distribution of planets and it is marginalized over the
empirical distribution of stellar parameters.
It is possible to relax this assumption and apply different distributions by
re-weighting the simulations used to generate this figure.
Therefore, alongside this \paper, we publish the full list of injection
simulations\footnote{SOMEURL} to be used for population inference (occurrence
rate measurements).
In \fig{completeness}, we also show the detection efficiency---marginalized
over the same range of periods---as a function of stellar magnitude in the
\kepler\ bandpass as reported in the Ecliptic Plane Input Catalog
(EPIC\footnote{http://archive.stsci.edu/k2/epic.pdf}).

@@

% (Note: C1 data came out the week between Christmas and New Years, so Charbonneau
% didn't show anything from C1. Based on when he came down to visit you guys, it was
% very likely Andrew's HIP 116454 he showed).

% That's correct. Everyone except for Hogg knows that so I don't think that we
% need to say anything here :-)
